---
title: "Joe_Rovalino_Data607_wk#1"
author: "Joe Rovalino"
date: "8/29/2019"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

Relevant Information:
    This data set includes descriptions of hypothetical samples
    corresponding to 23 species of gilled mushrooms in the Agaricus and
    Lepiota Family (pp. 500-525).  Each species is identified as
    definitely edible, definitely poisonous, or of unknown edibility and
    not recommended.  This latter class was combined with the poisonous
    one.  The Guide clearly states that there is no simple rule for
    determining the edibility of a mushroom; no rule like ``leaflets
    three, let it be'' for Poisonous Oak and Ivy.

 
```{r}
df <- read.table("https://raw.githubusercontent.com/jrovalino/Data607/master/agaricus-lepiota.data", 
                 header = FALSE, sep=",", stringsAsFactors=FALSE)
#nrow(df)
#ncol(df)
str(df)
#head(df)
#summary(df)
dim(df)
colnames(df)
```
Going to create a subset DF with better names. First going to change the columns names to something more descriptive then V#. Found the example to do this on following:
https://www.datanovia.com/en/lessons/rename-data-frame-columns-in-r/

```{r}
library(tidyverse)
subdf <- df %>% 
  rename(
    EDIBLE = V1,
    CONVEX = V2,
    SMOOTH = V3,
    WHITE = V4,
    BRUISES = V5,
    ALMOND = V6,
    FREE = V7,
    CROWDED = V8,
    NARROW = V9,
    WHITE = V10,
    TAPERING = V11,
    BULBOUS = V12,
    SMOOTH = V13,
    SMOOTH = V14,
    WHITE = V15,
    WHITE = V16,
    PARTIAL = V17,
    WHITE = V18,
    ONE = V19,
    PENDANT = V20,
    PURPLE = V21,
    SEVERAL = V22,
    WOODS = V23 
    )


```

Next step: You should include the column that indicates edible or poisonous and three or four other columns. The rename step was already performed above using dplyr::rename(). So now will create the dataframe with 4 columns inclusive of Edible 
```{r}
Four_col_df <- subdf[, c(1,3,5,7)]
head(Four_col_df)
```
